New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2022-10-19 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
upload data

---
title             : "New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?"
shorttitle        : "Measuring novice and expert teachers' heart rate"

@@

```
# Introduction

Prospective teachers experience the first five years as a particular professional challenge, as they are associated with a high workload (e.g., class size, poor student behavior) and resulting stress in the teaching profession [@struyven2014teachers].

Psychosomatic stress symptoms, such as increasing heart rate, result from an interaction of situational stressors and person-specific available resources ["transactional stress model"; @lazarus1987transactional; @obbarius2021modified]. If teachers are exposed to a stressful teaching-learning environment for a long time and do not have the sufficient resources and coping strategies, this can lead to burnout.

Fisher (2011) showed in her study of 400 secondary school teachers that burnout scores differed significantly between novice and experienced teachers, with novices having higher burnout scores. In addition, she found that a low number of years of professional experience was a statistically significant predictor of stress in the teaching profession, along with job satisfaction and burnout.

In addition to self-reported indicators of stress (e.g., emotional exhaustion), psychophysiological indicators (e.g., heart rate) are becoming increasingly important in research. Heart rate as the number of heart contractions per minute [@Löllgen2015] is an important indicator of physical or emotional stress. Increased workload is associated with increased heart rate [@sachs2014physiologische]. Arguably, physiological data provide a more objective and non-reactive measure of stress in the classroom (Runge et al., 2020). However, in an educational context, this requires the use of low-cost, non-invasive instruments. Fitness trackers worn on the wrist could fill this research gap [@ferguson2015validity].

## Aim of the study
The aim of the study was to uncover differences between 25 experienced and 25 inexperienced teachers on the physical and emotional demands during a 15-minute micro-teaching unit by measuring their heart rate using a fitness watch (Fitbit Charge 4). As the fitness watch was put on at the beginning of the survey and was not taken off until the entire data collection was completed, the heart rate could be measured in the resting and arousal states. In addition, the watch recorded the subjects' movement activity to determine how many steps were taken during the lesson. The practicality of the FitBit for classroom research is discussed.

@@

# exclude cases with no fitbit data
demo.data.raw <- demo.data %>% filter(!ID %in% c("126",
                                                 "132"
                                                 )
                                      )

@@

```{r}
# Initial Preparations
## Run following Code if and only if new data is added to the initial data.

source(file = "data.wrangling.R")

# Mean, SD, t-test & Cohen D for experts & novices
# novices
mean_nov <- 
  df_heart_aggr %>%
  filter(status == "Novice" ) %>% 
  pull(mean) %>% 
  mean() %>% 
  round(., digits = 0)

sd_nov <- 
  df_heart_aggr %>%
  filter(status == "Novice") %>% 
  pull(mean) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_exp <-
  df_heart_aggr %>%
  filter(status == "Expert") %>% 
  pull(mean) %>% 
  mean() %>% 
  round(., digits = 0)

sd_exp <- 
  df_heart_aggr %>%
  filter(status == "Expert") %>% 
  pull(mean) %>% 
  sd() %>% 
  round(., digits = 0)

# t-test for expertise differences
t.test(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
       y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"])

# effect size for expertise differences
d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
               y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
               na.rm = TRUE)

# Plots

df_heart_all <-
  read_rds(file = "data/heart_all.rds") |>
  mutate(status = factor(status,
                         levels = c("Expert","Novice"),
                         labels = c("Expert","Novice")
                         )
         )

df_heart_min <-
  read_rds(file = "data/heart_min.rds")

df_heart_aggr <-
  read_rds(file = "data/heart_aggr.rds") |>
  mutate(status = factor(status,
                         levels = c("Novice","Expert"),
                         labels = c("Novice","Expert")
                         )
         )

plot_flow_leg <-
ggplot(data = df_heart_all,
       mapping = aes(x = Time,
                     y = `Heart Rate`
                     )
       ) +
  xlim(0, 600) +
  geom_smooth(mapping = aes(color = status),
              method = "loess") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in Seconds)",
       y = "Heart Rate\n(in Beats per Minute)") +
  ggtitle("Experts' and novices' heart rate per phase") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 10),
        strip.text = element_text(size = 16),
        plot.title = element_text(size = 20, 
                                  face = "bold")) +
  facet_grid(cols = vars(Type),
             scales = "free_x")

legend <- cowplot::get_legend(plot_flow_leg)

# saving plot 
ggsave(plot = plot_flow_leg,
       filename = "Plots/plot_flow_leg.svg",
       height = 5,
       width = 8,
       units = "in")

############### BOX PLOT #############

##### Box 1 Plot ##### 
plot_box1 <- 
ggplot(data = df_heart_aggr,
       mapping = aes(x = Type,
                     y = mean,
                     color = status
                     )
       ) +
  geom_boxplot(color = "darkgrey",
               fill = "grey") +
  geom_line(data = filter(df_heart_aggr,
                          status == "Novice"),
            mapping = aes(x = Type,
                          y = mean,
                          group = as_factor(ID)
                          ),
            linetype = 1,
            alpha = 0.5
            ) +
  geom_line(data = filter(df_heart_aggr,
                          status == "Expert"),
            mapping = aes(x = Type,
                          y = mean,
                          group = as_factor(ID)
                          ),
            linetype = 6,
            alpha = 0.5
            ) +
  geom_point(size = 2,
             alpha = 0.5) +
  labs(x = "",
       y = "Average Heart Rate\n(in Beats per Minute)") +
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        strip.text = element_blank(),
        legend.position = "none",
        axis.text.x = element_blank()
        ) +
  aes(fill = Type)

plot_box1

##### Box 2 Plot ##### 
plot_box <-
  ggplot(data = df_heart_aggr,
         mapping = aes(x = Type,
                       y = mean)) + 
  geom_boxplot(mapping = aes(fill = status),
               outlier.shape = NA) +
  geom_point(mapping = aes(shape = status),
             alpha = 0.5,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  labs(x ="",
       y = "Average Heart Rate\n(in Beats per Minute)") + 
  ggtitle("Experts' and novices' heart rate per phase") +
  scale_fill_brewer(palette  = "RdBu") +  
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 10),
        strip.text = element_text(size = 16),
        plot.title = element_text(size = 20, 
                                  face = "bold"))

plot_box

# saving plot 
ggsave(plot = plot_box,
       filename = "Plots/plot_box.svg",
       height = 5,
       width = 8,
       units = "in")

@@

```{r}
df_steps <- read_rds(file = "data/steps.rds")
set.seed(5678)
ggplot(data = df_steps,
       mapping = aes(x = type,
                     y = Steps
                     )
       ) +
  geom_boxplot(mapping = aes(color = type),
               fill = "grey",
               alpha = 0.6) +
  geom_jitter(mapping = aes(color = type),
              alpha = 0.9,
              width = 0.3) +
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  labs(x = "",
       y = "Steps During\nMain Phase") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
        )

### Validation of steps
# selecting some rows at random with sample_n()
sample_n(df_steps, 6)

# random ID Output:
# Novices ID: 102, 125, 110
# Experts ID: 219, 218, 214

# Results from manual step counting:
# Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
# Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps

>>>>

---
title             : "New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?"
shorttitle        : "Using fitbit to measure teachers' heart rate"

@@

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Introduction
Physiological data such as heart rate are becoming increasingly important in research on stress experience. They represent an important indicator of physical or emotional stress, as increased workload is associated with increased heart rate [@sachs2014physiologische]. Furthermore, they allow a more objective recording of stress than self-reports [@rungeusing]. However, capturing heart rate in an educational context requires the use of low-cost and non-invasive instruments. Fitness trackers worn on the wrist have the potential to be such a useful tool [@ferguson2015validity].

To date, there is still little evidence on the usefulness of heart rate measurements using fitness trackers in teaching and learning settings [@ertzberger2016use; @lowe2016educational]. @rungeusing alone examined teacher stress in a relatively small sample (*N* = 4 teachers) and showed that high heart rate, high step count, and little sleep indicate more stress in teachers.

Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of stress. Since, among other things, greater professional experience is associated with lower feelings of stress in the teaching profession [@fisher2011factors], this study will also consider the heart rate measurements of experienced and inexperienced teachers.

## Aim of the study
Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases and (2) between experienced and inexperienced teachers. We expected heart rates to be higher in the arousal phase than in the rest phases and exploratively examine whether experienced teachers have lower heart rates and more steps compared to inexperienced teachers.

@@

# exclude cases with no fitbit data
demo.data <- demo.data.raw %>% filter(!ID %in% c("126",
                                                 "132"
                                                 )
                                      )

@@

```{r}
# Initial Preparations

## Run following Code only if new data is added to the initial data.
# 
# source(file = "data.wrangling.R")
# 
# # aggregate data 
# df_heart_all <-
#   read_rds(file = "data/heart_all.rds") |> 
#   mutate(status = factor(status,
#                          levels = c("Expert","Novice"),
#                          labels = c("Expert","Novice")
#                          )
#          )
# 
# df_heart_min <-
#   read_rds(file = "data/heart_min.rds")
# 
# df_heart_aggr <- 
#   read_rds(file = "data/heart_aggr.rds") |> 
#   mutate(status = factor(status,
#                          levels = c("Novice","Expert"),
#                          labels = c("Novice","Expert")
#                          )
#          )
# 
# 
# # Mean, SD, t-test & Cohen D for experts & novices
# # novices
# mean_nov <- 
#   df_heart_aggr %>%
#   filter(status == "Novice" ) %>% 
#   pull(mean) %>% 
#   mean() %>% 
#   round(., digits = 0)
# 
# sd_nov <- 
#   df_heart_aggr %>%
#   filter(status == "Novice") %>% 
#   pull(mean) %>% 
#   sd() %>% 
#   round(., digits = 0)
# 
# # experts
# mean_exp <-
#   df_heart_aggr %>%
#   filter(status == "Expert") %>% 
#   pull(mean) %>% 
#   mean() %>% 
#   round(., digits = 0)
# 
# sd_exp <- 
#   df_heart_aggr %>%
#   filter(status == "Expert") %>% 
#   pull(mean) %>% 
#   sd() %>% 
#   round(., digits = 0)
# 
# # t-test for expertise differences
# t.test(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
#        y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"])
# 
# 
# # effect size for expertise differences
# d_heartrate <- CohenD(x = df_heart_aggr$mean[df_heart_aggr$status == "Expert"],
#                y = df_heart_aggr$mean[df_heart_aggr$status == "Novice"],
#                na.rm = TRUE)
# 
# 
# # Plots
# 
# plot_flow_leg <-
# ggplot(data = df_heart_all,
#        mapping = aes(x = Time,
#                      y = `Heart Rate`
#                      )
#        ) +
#   xlim(0, 600) +
#   geom_smooth(mapping = aes(color = status),
#               method = "loess") +
#   scale_color_viridis_d(option = "A",
#                         end = 0.8) +
#   scale_linetype_manual(values = c(1, 6)) +
#   labs(x = "Time (in Seconds)",
#        y = "Heart Rate\n(in Beats per Minute)") +
#   ggtitle("Experts' and novices' heart rate per phase") +
#   theme_minimal() +
#   theme(text = element_text(family = "serif"),
#         legend.text = element_text(size = 15),
#         legend.title = element_blank(),
#         axis.text.x = element_text(size = 12),
#         axis.text.y = element_text(size = 10),
#         strip.text = element_text(size = 16),
#         plot.title = element_text(size = 20, 
#                                   face = "bold")) +
#   facet_grid(cols = vars(Type),
#              scales = "free_x")
# 
# # saving plot 
# ggsave(plot = plot_flow_leg,
#        filename = "plots/plot_flow_leg.svg",
#        height = 5,
#        width = 8,
#        units = "in")

@@

```{r}
# df_steps <- read_rds(file = "data/steps.rds")
# set.seed(5678)
# ggplot(data = df_steps,
#        mapping = aes(x = type,
#                      y = Steps
#                      )
#        ) +
#   geom_boxplot(mapping = aes(color = type),
#                fill = "grey",
#                alpha = 0.6) +
#   geom_jitter(mapping = aes(color = type),
#               alpha = 0.9,
#               width = 0.3) +
#   scale_color_viridis_d(option = "A",
#                        end = 0.8) +
#   labs(x = "",
#        y = "Steps During\nMain Phase") +
#   theme_minimal() +
#   theme(text = element_text(family = "serif"),
#         legend.title = element_blank(),
#         axis.text.x = element_blank(),
#         axis.ticks.x = element_blank()
#         )
# 
# ### Validation of steps
# # selecting some rows at random with sample_n()
# sample_n(df_steps, 6)
# 
# # random ID Output:
# # Novices ID: 102, 125, 110
# # Experts ID: 219, 218, 214
# 
# # Results from manual step counting:
# # Novices ID: 110 -> 178 steps; 102 -> 219 steps; 125 -> 319 steps
# # Experts ID: 214 -> 437 steps; 218 -> 195 steps; 219 -> 530 steps

### 2022-10-19 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
upload data

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{heart rate; photoplethysmography; wearable electronic device; expertise differences \newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\shorttitle{Measuring novice and expert teachers' heart rate}

@@

Prospective teachers experience the first five years as a particular professional challenge, as they are associated with a high workload (e.g., class size, poor student behavior) and resulting stress in the teaching profession (Struyven \& Vanthournout, 2014).

Psychosomatic stress symptoms, such as increasing heart rate, result from an interaction of situational stressors and person-specific available resources {[}``transactional stress model''; Lazarus and Folkman (1987); Obbarius, Fischer, Liegl, Obbarius, and Rose (2021){]}. If teachers are exposed to a stressful teaching-learning environment for a long time and do not have the sufficient resources and coping strategies, this can lead to burnout.

Fisher (2011) showed in her study of 400 secondary school teachers that burnout scores differed significantly between novice and experienced teachers, with novices having higher burnout scores. In addition, she found that a low number of years of professional experience was a statistically significant predictor of stress in the teaching profession, along with job satisfaction and burnout.

In addition to self-reported indicators of stress (e.g., emotional exhaustion), psychophysiological indicators (e.g., heart rate) are becoming increasingly important in research. Heart rate as the number of heart contractions per minute (Löllgen, 2015) is an important indicator of physical or emotional stress. Increased workload is associated with increased heart rate (Sachs, 2014). Arguably, physiological data provide a more objective and non-reactive measure of stress in the classroom (Runge et al., 2020). However, in an educational context, this requires the use of low-cost, non-invasive instruments. Fitness trackers worn on the wrist could fill this research gap (Ferguson, Rowlands, Olds, \& Maher, 2015).

@@

The aim of the study was to uncover differences between 25 experienced and 25 inexperienced teachers on the physical and emotional demands during a 15-minute micro-teaching unit by measuring their heart rate using a fitness watch (Fitbit Charge 4). As the fitness watch was put on at the beginning of the survey and was not taken off until the entire data collection was completed, the heart rate could be measured in the resting and arousal states. In addition, the watch recorded the subjects' movement activity to determine how many steps were taken during the lesson. The practicality of the FitBit for classroom research is discussed.

@@

XXX fitbit data exclusion XXX

The sample consisted of \emph{N} = 41 participants with \emph{n} = 16 expert teachers and \emph{n} = 25 novice teachers.

@@

The expert teachers (9 women; 56.25\%) had a mean age of 41.40 years (\emph{SD} = 10.70; range: 27-59) and an average teaching experience of 13.60 years (\emph{SD} = 12.80; range: 2-37).
18.75\% of the experts were primary school teachers and 81.25\% were secondary school teachers. 56\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (16 women; 64\%) had a mean age of 23.40 years (\emph{SD} = 1.80; range: 20-27) with an average teaching experience of 0 years. On average, the student teachers were in their 7.30 semester (\emph{SD} = 2.60; range: 3-11). Furthermore, they had an average teaching experience of 11.20 teaching units à 45min (\emph{SD} = 8.10; range: 0-36) through the internships during their studies.
20\% of the novices were studying to become primary school teachers, 68\% to become secondary school teachers and 12\% to become special education teachers. 88\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

XXX Data and data wrangling need to be imported XXX

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-lazarus1987transactional}{}}%
Lazarus, R. S., \& Folkman, S. (1987). Transactional theory and research on emotions and coping. \emph{European Journal of Personality}, \emph{1}(3), 141--169.

\leavevmode\vadjust pre{\hypertarget{ref-Luxf6llgen2015}{}}%
Löllgen, H. (2015). Herzfrequenz und blutdruck. In J. Niebauer (Ed.), \emph{Sportkardiologie} (pp. 87--105). Berlin, Heidelberg: Springer Berlin Heidelberg. \url{https://doi.org/10.1007/978-3-662-43711-7_9}

\leavevmode\vadjust pre{\hypertarget{ref-obbarius2021modified}{}}%
Obbarius, N., Fischer, F., Liegl, G., Obbarius, A., \& Rose, M. (2021). A modified version of the transactional stress concept according to lazarus and folkman was confirmed in a psychosomatic inpatient sample. \emph{Frontiers in Psychology}, \emph{12}, 584333.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-struyven2014teachers}{}}%
Struyven, K., \& Vanthournout, G. (2014). Teachers' exit decisions: An investigation into the reasons why newly qualified teachers fail to enter the teaching profession or why those who do enter do not continue teaching. \emph{Teaching and Teacher Education}, \emph{43}, 37--45.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{heart rate; photoplethysmography; wearable electronic device; expertise differences\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\shorttitle{Using fitbit to measure teachers' heart rate}

@@

Physiological data such as heart rate are becoming increasingly important in research on stress experience. They represent an important indicator of physical or emotional stress, as increased workload is associated with increased heart rate (Sachs, 2014). Furthermore, they allow a more objective recording of stress than self-reports (Runge, Haarman, \& Fisher, n.d.). However, capturing heart rate in an educational context requires the use of low-cost and non-invasive instruments. Fitness trackers worn on the wrist have the potential to be such a useful tool (Ferguson, Rowlands, Olds, \& Maher, 2015).

To date, there is still little evidence on the usefulness of heart rate measurements using fitness trackers in teaching and learning settings (Ertzberger \& Martin, 2016; Lowe, 2016). Runge et al. (n.d.) alone examined teacher stress in a relatively small sample (\emph{N} = 4 teachers) and showed that high heart rate, high step count, and little sleep indicate more stress in teachers.

Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of stress. Since, among other things, greater professional experience is associated with lower feelings of stress in the teaching profession (Fisher, 2011), this study will also consider the heart rate measurements of experienced and inexperienced teachers.

@@

Against this background, we investigated whether heart rate measurements using fitness trackers in a controlled teaching-learning setting are suitable to map differences between (1) anticipation, arousal, and rest phases and (2) between experienced and inexperienced teachers. We expected heart rates to be higher in the arousal phase than in the rest phases and exploratively examine whether experienced teachers have lower heart rates and more steps compared to inexperienced teachers.

@@

The sample consisted of \emph{N} = 51 participants with \emph{n} = 19 expert teachers and \emph{n} = 32 novice teachers.

The data of two participants (two novices, XXX experts) were excluded from the analyses due to insufficient data quality.

@@

The expert teachers (11 women; 57.89\%) had a mean age of 41.70 years (\emph{SD} = 10.40; range: 27-59) and an average teaching experience of 13.70 years (\emph{SD} = 12.40; range: 2-37).
15.79\% of the experts were primary school teachers and 84.21\% were secondary school teachers. 47\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (23 women; 71.88\%) had a mean age of 23 years (\emph{SD} = 1.90; range: 19-27) with an average teaching experience of 0 years. On average, the student teachers were in their 7 semester (\emph{SD} = 2.60; range: 3-11). Furthermore, they had an average teaching experience of 10.30 teaching units à 45min (\emph{SD} = 7.70; range: 0-36) through the internships during their studies.
21.88\% of the novices were studying to become primary school teachers, 62.50\% to become secondary school teachers and 15.62\% to become special education teachers. 90.62\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-ertzberger2016use}{}}%
Ertzberger, J., \& Martin, F. (2016). Use of fitness bands by teachers in the classroom. \emph{TechTrends}, \emph{60}(4), 392--397.

@@

\leavevmode\vadjust pre{\hypertarget{ref-lowe2016educational}{}}%
Lowe, H. (2016). Educational behavior apps and wearable devices: Current research and prospects. \emph{Educational Technology}, 30--33.

@@

\leavevmode\vadjust pre{\hypertarget{ref-rungeusing}{}}%
Runge, N., Haarman, S., \& Fisher, M. H. (n.d.). \emph{Using fitbit fitness trackers to measure teacher stress and coping}.

@@
